\chapter*{Possible Approach}


\section*{Hard- and Softwarestack}

The mobile application will be developed for Android and tested using a Google Pixel 7.
The implementation will be carried out in Java/Kotlin using the Android Studio integrated development environment (IDE).
The Google ARCore SDK will be used to access depth information about a scene.
The SDK is available by default -- no additional libraries are required.

Algorithms will be implemented in C\texttt{++} in the \texttt{procedural-augmented-reality} project provided by Prof. Dr. Phillipp Jenke.
This project will be integrated into the application and interfaced with Kotlin through a binding layer.


\section*{Approach Outline}
The ARCore Raw Depth API provides depth images with corresponding confidence images and RGB images~\parencite{google_llc_arcore_doc}.
These images also allow for the creation of a point cloud by projecting each pixel into three-dimensional space, utilizing the camera's intrinsics~\parencite{google_llc_codelab_raw_depth}.

The obtained data (RGB Images, Depth Images, Point Clouds) can serve as the foundation for detecting geometric primitives.
Various algorithms suitable for this task are compared in ~\parencite{kaiser_survey_2019}.
For instance, an algorithm based on RANSAC like~\parencite{schnabel_efficient_2007}
can utilize the point cloud to identify geometric primitives.
Additionally, the confidence images from the Raw Depth API can be employed to improve the detection outcomes.

\section*{Potential pitfalls}
As the development device, Google Pixel 7, does not have a depth sensor,
the Depth API will exclusively utilize depth-from-motion techniques to derive depth information from camera images.
However, it is important to note that camera-based depth-from-motion has limitations
when it comes to detecting depth in objects with minimal texture, such as walls.
This drawback could potentially present challenges.
For instance, if the objective were to recognize objects like boxes or spheres that lack texture,
the accuracy of depth information obtained from the Depth API may not be sufficient for accurate recognition.
\parencite{google_llc_arcore_doc}

